A Machine Profile Summary

### 2022-06-14 MachineSummary/MachineSummary.Rmd
added gb vs gib

There may be multiple terms used to describe some of the information we want, as
well as different interpretations of some of the units of measure. For example
"Gigabytes", or GB, may be $1000^3$ or $1024^3$ bytes. ?? AB? Is that correct?

>>>>

There may be multiple terms used to describe some of the information we want, as
well as different interpretations of some of the units of measure. For example
"Gigabytes" may be $1000^3$ or $1024^3$ bytes. To settle the ambiguity, the
international standard *IEC 80000-13:2008 Quantities and units - Part 13: Information science and technology*(??ref https://en.wikipedia.org/wiki/Gigabyte, https://en.wikipedia.org/wiki/ISO/IEC_80000#Part_13:_Information_science_and_technology) defines 1 Gigabyte (1 GB) as 1000^3 bytes, whereas 1 Gibibyte (1 GiB) as 1024^3 bytes.

<!-- ?? AB? Is that correct? -->
